global-model (ODE)

### 2015-09-16 documentation/interactive_spexmodel.Rmd
update shiny docs

inputPanel(
  sliderInput("rho_1", label = "initial plant cover:",
              min = 0.0, max = 1, value = 0.9, step = 0.01)
  )

@@

spexmodel <- runCA(input$rho_1, parms, delta = 0.2, t_max = 60, t_min = 50, t_eval = 5, isstable = 0.001, saveeach = 1)

lines(spexmodel$rho_one ~ spexmodel$time, col = "grey50")

meanfield <-as.data.frame( ode(ini_rho(input$rho_1), func = odesys_mean, times = exp(seq(0,4,length = 100))-1, parms = parms))
lines(rho_1 ~ time , data = meanfield, col = "red3")

>>>>

inputPanel(

  checkboxInput("meanfield", "Meanfield model", FALSE),
  checkboxInput("pair", "Pair-approximation model", TRUE),
  checkboxInput("ca", "Cellular automata", TRUE),
  sliderInput("rho_1", label = "initial plant cover:",
              min = 0.0, max = 1, value = 0.9, step = 0.01)
  )

@@

if(input$ca) {
  spexmodel <- runCA(input$rho_1, parms, delta = 0.2, t_max = 60, t_min = 50, t_eval = 5, isstable = 0.001, saveeach = 1)
  lines(spexmodel$rho_one ~ spexmodel$time, col = "grey50")
}

if(input$meanfield) {
  meanfield <-as.data.frame( ode(ini_rho(input$rho_1), func = odesys_mean, times = exp(seq(0,4,length = 100))-1, parms = parms))
  lines(rho_1 ~ time , data = meanfield, col = "red3")
}

### 2015-09-16 documentation/interactive_spexmodel_attractor.Rmd
update shiny docs

@@

workstation <-  list(host = "162.38.184.118", user = "schneider",
                     rscript = "/usr/lib/R/bin/Rscript",
                     snowlib = "/usr/lib/R/library")

workerlist <- c(rep("localhost", times = 10))

cl <- makeSOCKcluster(workerlist, master="162.38.184.88", outfile='out_messages.txt')

@@

@@

  source("../code/simfunctions.r")

@@

#iterations$f[iterations$f < iterations$b] <- iterations$b[iterations$f < iterations$b]

attractor(parms, localvals = FALSE, pairapprox = TRUE, meanfield = FALSE, rho_1_ini = seq(0,1, length = 21) )

# if(input$gradient == "b") plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))
# if(input$gradient == "L") plot(rho_1 ~ L, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

>>>>

```{r, echo=FALSE, warning=FALSE}

@@

workstation <-  list(host = "162.38.184.118", user = "florian",
                     rscript = "/usr/lib/R/bin/Rscript",
                     snowlib = "/usr/lib/R/library")

workerlist <- c(rep(workstation, times = 7))

cl <- makeSOCKcluster(workerlist, outfile='out_messages.txt')

@@

inputPanel(
  selectInput("model",
      label = "model type:",
      choices = c("meanfield", "pairapprox"),
      selected = 1
  )
)

@@

  source("C:/Users/florian.schneider/Documents/projects/CAS02_livestock/code/simfunctions.r")

@@

#iterations$f[iterations$f < iterations$b] <- iterations$b[iterations$f < iterations$b]
if(input$model == "meanfield") attractor(parms, localvals = TRUE, pairapprox = FALSE, meanfield = TRUE, rho_1_ini = seq(0,1, length = 11) )

if(input$model == "pairapprox") attractor(parms, localvals = FALSE, pairapprox = TRUE, meanfield = FALSE, rho_1_ini = seq(0,1, length = 11) )
# if(input$gradient == "b") plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))
# if(input$gradient == "L") plot(rho_1 ~ L, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

### 2015-09-16 documentation/interactive_spexmodel_bifurcations.Rmd
update shiny docs

 if(input$gradient == "b") bifurcation(parms,"b", c(0,1))
 if(input$gradient == "L") bifurcation(parms, "L", c(0,12))

} )
```

>>>>

 if(input$gradient == "b") { 
#par(mfrow =c(2,2))

   bifurcation(parms,"b", c(0,1)) -> over_b

#over_b$pairapprox$q_11 <- over_b$pairapprox$rho_11/over_b$pairapprox$rho_1
#over_b$pairapprox$q_11[is.na(over_b$q_11)] <- 0

#  plot(over_b$pairapprox$b, over_b$pairapprox$q_11, pch = 20,  cex = 0.5, ylim = c(0,1), xlim = c(0,1))

 # plot(over_b$pairapprox$rho_11, over_b$pairapprox$q_11, pch = 20,  cex = 0.5, ylim = c(0,1), xlim = c(0,1))
#abline(a = 0, b = 1, lty = 3, col = "#D0D0D0")
#points(0,0, pch=20, col = "white", cex = 2)
# points(0,0, pch=20, cex = 0.5)

 } 
 if(input$gradient == "L") {

#par(mfrow =c(2,2))

   bifurcation(parms, "L", c(0,12)) -> over_b

#over_b$pairapprox$q_11 <- over_b$pairapprox$rho_11/over_b$pairapprox$rho_1
#over_b$pairapprox$q_11[is.na(over_b$q_11)] <- 0

#  plot(over_b$pairapprox$b, over_b$pairapprox$q_11, pch = 20,  cex = 0.5, ylim = c(0,1), xlim = c(0,1))

#  plot(over_b$pairapprox$rho_11, over_b$pairapprox$q_11, pch = 20,  cex = 0.5, ylim = c(0,1), xlim = c(0,1))
#abline(a = 0, b = 1, lty = 3, col = "#D0D0D0")
#points(0,0, pch=20, col = "white", cex = 2)
# points(0,0, pch=20, cex = 0.5)

   }

} )
